### 2010-06-22 paper/IIWAS2010/content/introduction.tex
small changes to intro

The Morpheus system employs two types of users. The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser.  This web browser is fitted with a browser plug-in that stores the query and collects information necessary to revisit the pathways to the answer. It also allows the user to highlight answers and other metadata.
The second user, searches the Morpheus system much
like a typical search engine with a natural language interface. She can type a
question in a text box and receive a response from the system. The system
exploits previously answered queries to answer new questions.

To exploit the prior searches one should represent queries in an elegant way so
that similar queries can be found efficiently and their stored search path
revisited to produce answer to the user. Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}. A category represents a \textit{topic} or \textit{class} that a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.

>>>>

The Morpheus system employs two types of users. The first user type, or \textit{guide user}, types queries into the Morpheus interface and subsequently searches for an answer to the query in an instrumented web browser. This web browser is fitted with a browser plug-in that stores query and collects necessary information to revisit the pathways to the query answer. It also allows the user to highlight answers and other metadata. The second user type, or \textit{regular user} searches the Morpheus system much like a typical search engine with a natural language interface. He or she can type a question in a text box and receive a response from the system. In this case, the Morpheus system exploits already answered queries to answer new questions.

To utilize the prior searches one should represent queries in an elegant way so that similar queries can be found efficiently and their stored search path revisited to generate an answer to the user. Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It includes a user query in natural-language format, relevant terms for the query, place holders for the term \textit{categories}. A \textit{category} represents a topic or class that a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.
